In this section, we discuss the construction of the LSM-buffer benchmark, the design of the experimental framework, and our evaluation methodology. 



\subsection{Buffer Implementation}
The buffer in LSM-trees serve as a staging area for writes (inserts, updates, and deletes) before they are flushed to disk. 
Batching inserts in the main memory allows for amortizing the cost of writes, every flush writes approximately $P\cdot B$ entries to the disk, where $P$ is the size of the memory buffer in disk pages and $B$ is the average number of key-value pairs in every page. 
\red{Table~\ref{table:terms} gives a list of terms we use throughout this paper.}
Retaining the ingested entries in the buffer also allows future point queries on the recently ingested entries to be returned directly from the buffer, without any disk access. 
This can significantly improve the throughput for point queries on ``hot'' data. 
Below, we discuss the design and configuration of the four memory buffer implementations we use for the benchmark.

\Paragraph{Vector} 
We experiment with two \textit{vector} implementations of the memory buffer. 
The first is a \textit{dynamic vector} that is implemented as an automatically re-sizing array. 
A \textit{dynamic vector} ensures that the data in the buffer is stored in contiguous memory locations. 
Inserts to such a \textit{vector} is appended to the array if there is available space. 
Otherwise, the array size is doubled through re-sizing before appending the new entry. 
While appending inserts allows for a high throughput for writes, the cost of point queries can become prohibitively high as they may need to scan the entire buffer. 
Production systems, using a \textit{dynamic vector} implementation for the buffer, thus, sort the buffer every time there is a point query in the workload. 
The optimistic outlook here is that for future point queries that precede an insert, the target entry can be found using binary search. 
A dynamically allocated \textit{vector} suffers from high latency spikes that may be triggered by (i) re-sizing of the buffer or (ii) sorting the buffer contents while enabling a point query. 
The second implementation of a \textit{fixed-sized vector} requires allocating the designated memory space upfront, but is better suitable for latency-sensitive applications as it offers predictable performance with no latency spikes. 
Both \textit{vector} implementations has little memory overhead as they need to maintain minimal metadata. 

% However, its dependence on linear search $O(n)$ for indexing renders it less effective for point 
% queries and scans, as these operations necessitate sequential traversal of the \textit{vector}. The memory overhead for a 
% \textit{vector} is relatively minimal, requiring only additional space for resizing along with a modest amount of metadata. Due 
% to its lower memory demands, a \textit{vector} can potentially store more data, leading to fewer disk flushes. Nonetheless, 
% \textit{vectors} are not well-suited for handling point queries due to the linear search requirement. It can also
% slow down the write operations when the size of the \textit{vector} grows and it needs to be resized, for large
% buffer sizes (M). This problem can be mitigated by using a \textit{vector} of fixed size close to the write buffer.

\Paragraph{Skip-List} 
The default buffer implementation in many systems, such as RocksDB~\cite{Facebook2021} and LevelDB~\cite{GoogleLevelDB}, is \textit{skip-list}. 
A \textit{skip-list} is implemented as a hierarchical structure of linked-lists, where intermediate levels act as an index for the last level which stores the data in sorted order. 
\textit{Skip-lists} offer logarithmic $O(\log n)$ complexity for inserts, updates, deletes, as well as point queries. 
% Consequently, \textit{skip-lists} are exceptionally suited for achieving balanced read and write operations, as well as efficiently supporting fully ordered database scans.
However, the hierarchical structure of \textit{skip-lists} requires maintaining additional key-pointer pairs for indexing purposes, and this adds to the metadata overhead of the data structure. 
For example, a \textit{skip-list} with four levels, requires a memory of roughly $1.33\times$ of the data size. 

\begin{table}
    \begin{tabular}{|c|l|c|}
        \hline
        \textbf{Term} & \textbf{Description} & \textbf{Unit} \\
        \hline
        \textit{E} & entry size & Bytes \\
        \hline
        \textit{N} & total number of entries & entries \\
        \hline
        \textit{L} & number of levels & levels \\
        \hline
        \textit{B} & number of entries that fit into a page & entries \\
        \hline
        \textit{P} & size of buffer in pages & pages \\
        \hline
        \textit{T} & size ratio between adjacent levels &  \\
        \hline
        \textit{M} & main memory allocated to write buffer & Bytes \\
        \hline 
        \textit{Q} & number of point queries & queries \\
        \hline
        \textit{S} & number of range queries & queries \\
        \hline
        \textit{Y} & selectivity of range queries w.r.t N & percent \\ 
        \hline
        \textit{X} & prefix length & chars \\
        \hline
        \textit{H} & number of buckets in hash table & buckets \\
        \hline
    \end{tabular}
    \vspace{0.5em}
    \caption{Table of terms used throughout the paper.}
    \label{table:terms}
\end{table}


\Paragraph{Hash Skip-List} 
A memory buffer implemented as a \textit{hash skip-list} combines a hash table with \textit{skip-lists} within each bucket. 
The keys to be inserted are partitioned on their prefix (of a predetermined length) for bucket allocation, facilitating targeted insertions and pint queries through a combination of 
hashing and binary search. 
This structure offers superior performance for ingestion, point queries, as well as, range 
queries with very small selectivity, as the operations are typically limited to only a specific hash-bucket. 
Range queries with large selectivity, however, may span across multiple hash-buckets and, therefore, are may have a significantly higher latency.  
The design of the \textit{hash skip-list} involves configuring the number of buckets (\textit{H}) and specifying a prefix extractor, typically the first $l$ characters of the key. 
The role of the prefix extractor is to isolate the prefix from the key and hash it to the appropriate bucket. 
Each bucket, in turn, is a \textit{skip-list} that contains the key-value pairs. 
The entire key (including the prefix) is stored in the \textit{skip-list} as we need to facilitate range queries. 
% If a bucket is unused, it points to \texttt{nullptr}; otherwise, it points to the corresponding \textit{skip-list}. 
The point queries are realized by simply hashing the prefix to locate the target bucket and then by searching through \textit{skip-list}. 
The memory overhead of the \textit{hash skip-list} includes the additional space needed to maintain the hash table and the pointers to each \textit{skip-list}. 
Due to additional memory overhead, for the same memory budget, a \textit{hash skip-list} can buffer fewer key-value pairs compared to \textit{skip-list} and \textit{vector} before it is saturated. 
% This leads to which leads to more number of files to be flushed as file. 
% This limitation is addressed by the \textit{hash linked-list} which we will discuss in the next. The \textit{hash skip-list} is particularly well-suited for workloads
% involving a high volume of small range queries within specific key prefixes.

\Paragraph{Hash Linked-List} 
Similarly to the \textit{hash skip-list}, the \textit{hash linked-list} also uses a hash table framework; however, within each hash-bucket the entries are stored as a sorted singly \textit{linked-list}. 
This design is particularly tailored for efficiently handling range queries on specific key prefixes. 
It also offers the similar ingestion performance as the \textit{hash skip-list} with less memory overhead. 
For point queries, the \textit{hash linked-list} relies on linear search within each \textit{linked-list}, which may also reduce its efficiency compared to \textit{hash skip-list}. 
The \textit{hash linked-list} has a lower memory overhead compared to the \textit{hash skip-list}, primarily because it eschews the layered structure inherent to 
\textit{skip-lists}. 
% Consequently, this streamlined setup makes it an excellent choice for scenarios characterized by frequent small range queries within specific key prefixes, especially when each prefix is associated with a limited dataset.

% \subsection{Proposed Write Buffer} \lipsum[1]

% \Paragraph{Trie} \lipsum[1]

% \Paragraph{Tree} \lipsum[1]

\subsection{Evaluation Metric}
The choice of write buffer and its implementation have critical implications on the performance of LSM-engines. 
We will evaluate each implementation based on 
the below parameters. 
Note that the in-place updates occur only when the size of the key-value pair matches that of a 
previous insert.
\begin{itemize}[leftmargin=*,labelindent=0mm, itemsep=0.2\baselineskip]
    \item \textbf{Memory footprint}: This assesses the additional memory required by each write buffer implementation to 
    store $N$ entries, including both the metadata and the actual data (i.e.\ key-value pairs) within the write buffer.
    \item \textbf{Reads latency}: This focuses exclusively on the read operations performed within the write buffer to analyze 
    the performance of both point queries and range queries. The aim is to gauge the read efficiency of write buffer more accurately.
    \item \textbf{Writes latency}: Analogous to read efficiency, this evaluates the performance of write operations within 
    the write buffer, highlighting how effectively and swiftly data is written.
    \item \textbf{Flush count}: The high frequencies of flushing, particularly of smaller files, can augment write 
    amplification, thereby necessitating repetitive read-write cycles for identical datasets.
    \item \textbf{Compaction count}: The frequency of compactions is directly correlated with increase in write 
    amplification and read amplification, making it essential for understanding the overall performance of the LSM-tree.
\end{itemize}
The goal is to provide a detailed analysis of how various write buffer designs can affect overall database system 
efficiency, focusing more on memory usage, reads and write latency. By examining these key performance metrics, we 
intend to highlight the strengths and limitations of each write buffer implementation in the context of LSM-trees.