Here are the descriptions of all buffer implementations.

\begin{enumerate}
    \item \textbf{Skip-List:} The default datastructure implementation of a 
    write buffer is a skip-list.  A skip-list consists of layers of linked 
    lists, with each layer containing fewer elements (nodes) than the one below it. 
    The last layer contains all the elements in a sorted order like a regular linkedlist.
    The upper layers contain pointers that can be used to skip elements to reach target elements faster. 
    This probabilistic datastructure allows an $O(logn)$ search, insertion and deletion time.   
    
    In RocksDB, the SkipList is indexed using binary search that takes $O(logn)$ time.
    It provides general good performance for read, write, random access and sequential scan.
    SkipList based write buffer implementation naturally supports totally ordered DB scan.

    \item \textbf{HashSkipList:} HashSkipList is a hash table datastructure, where each
     bucket stores a skiplist. During insertion or lookup, the prefix of a key is used to
     identify the bucket that contains the target key. HashSkipList is indexed using a hash and 
     binary search operation. It is mainly useful for small range queries that lies within 
     a specific key prefix. However, range scan across multiple prefixes requires copy and 
     sort operation, making it expensive in terms of time and memory.

    \item \textbf{HashLinkList:} HashLinkList is also a hash table datastructure, where each
    bucket points to a sorted single linked list. 

    ###Range query within a specific key prefix and there are only a small number of rows 
    for each prefix###

    During insertion or lookup, the prefix of a key is used to identify the bucket that contains
    the target key. HashSkipList is indexed using a hash and linear search operation. Range scan 
    across multiple prefixes requires copy and sort operation, making it expensive in terms of time and memory.

    \item \textbf{Vector:} Vector is a dynamic array-like datastructure that can resize itself automatically
    upon insertion or deletion of an element. Vector is maintained as a contiguous storage so that iterators 
    can be used for traversal. Elements are inserted at the end of vectors, making them friendly for 
    write-heavy workloads. Vector is indexed using a linear search, making it costly for point queries and deletions.
\end{enumerate}